Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-07-24 manuscript/04-results.Rmd
Updated methods

### droughts(?)
[description of the 3 droughts in terms of timing, duration, severity, proportion of trees showing pointer year..?]

>>>>

### droughts(?)
description of the 3 droughts in terms of timing, duration, severity, proportion of trees showing pointer year..?. See

Proportion of all trees showing growth deficit for that year (meeting our threshold)
1966: 28.18% (20.88% if doing all trees 1964-1966)
1977:31.23%
1999: 26.21%

Proportion of species-canopy classes (e.g. fagr_canopy, quve_subcanopy) that have >50% of their trees showing a pointer year
1966: 22.73%
1977: 22.73%
1999: 13.64%
